Analysis-ready VCF at Biobank scale using Zarr

### 2025-01-25 paper.tex
Updates to Zarr table for AoU

\begin{table}
% \caption{Summary for VCF Zarr conversion of 
% Genomics England WGS data for chromosome 2 (78,195 samples, 59,880,903 variants),
% consisting of 44 fields and 2.54TiB of storage ($\sim$5X compression over gzipped VCF).
\caption{Summary for VCF Zarr conversion of 
Our Future Health genotype data for chromosome 22 (651,050 samples, 10,221
variants) consisting of 19 fields and 17GiB of storage ($\sim2.5$X compression
over shouce gzipped VCF).
% 42.3  / 17 = 2.4882
Here we use a chunk size of 1,000 variants $\times$ 10,000 samples and 
apply the BitRound(5) filter to the large floating point fields (see text for 
details).
For column details, see Table~\ref{tab-genomics-england-data}.
    \label{tab-ofh-data}}
\begin{tabular}{llS[table-format=3.2]S[table-format=4.1]S[table-format=3.2]}
\toprule
{Field} & {Type} & {Storage} & {Compress} & {\% Total} \\
\midrule
/call\_LRR & float32 & 8.41 GiB & 2.9 & 51.65\% \\
/call\_BAF & float32 & 6.14 GiB & 4.0 & 37.71\% \\
/call\_GS & float32 & 1021.24 MiB & 25.0 & 6.12\% \\
/call\_genotype & int8 & 663.97 MiB & 19.0 & 3.98\% \\
/call\_genotype\_mask & bool & 84.7 MiB & 150.0 & 0.51\% \\
/sample\_id & object & 3.19 MiB & 1.6 & 0.02\% \\
/call\_genotype\_phased & bool & 1.08 MiB & 5900.0 & 0.01\% \\
/variant\_id & object & 40.83 KiB & 2.0 & 0.00\% \\
/variant\_position & int32 & 39.03 KiB & 1.0 & 0.00\% \\
/variant\_allele & object & 20.71 KiB & 7.7 & 0.00\% \\
/variant\_filter & bool & 12.55 KiB & 0.8 & 0.00\% \\
/variant\_quality & float32 & 4.51 KiB & 8.8 & 0.00\% \\
/variant\_contig & int8 & 4.51 KiB & 2.2 & 0.00\% \\
/contig\_id & object & 4.51 KiB & 0.0 & 0.00\% \\
/variant\_id\_mask & bool & 4.5 KiB & 2.2 & 0.00\% \\
/contig\_length & int64 & 4.5 KiB & 0.0 & 0.00\% \\
/filter\_id & object & 4.43 KiB & 0.0 & 0.00\% \\
\bottomrule
\end{tabular}
\end{table}

@@

\begin{table}
\caption{Summary for a selection of the largest VCF Zarr columns
    for the All of Us exome-like data. The chunk size is
    1,000 variants $\times$ 10,000 samples.
    For column details, see Table~\ref{tab-genomics-england-data}.
    \label{tab-auo-data}}
\begin{tabular}{llS[table-format=3.2]S[table-format=4.1]S[table-format=3.2]}
\toprule
{Field} & {Type} & {Storage} & {Compress} & {\% Total} \\
\midrule
/call\_LAD & int16 & 2.26 GiB & 290.0 & 27.85\% \\
/call\_GQ & int8 & 1.89 GiB & 87.0 & 23.29\% \\
/call\_LA & int8 & 1.24 GiB & 260.0 & 15.28\% \\
/call\_genotype & int8 & 914.22 MiB & 370.0 & 11.00\% \\
/call\_RGQ & int16 & 729.57 MiB & 460.0 & 8.78\% \\
/call\_genotype\_mask & bool & 606.02 MiB & 550.0 & 7.29\% \\
/call\_FT & object & 498.61 MiB & 2700.0 & 6.00\% \\
\bottomrule
\end{tabular}
\end{table}

>>>>

\begin{table}
\caption{Summary for VCF Zarr conversion of 
Our Future Health genotype data for chromosome 22 (651,050 samples, 10,221
variants) consisting of 19 fields and 17GiB of storage ($\sim2.5$X compression
over source gzipped VCF).
% 42.3  / 17 = 2.4882
Here we use a chunk size of 1,000 variants $\times$ 10,000 samples and 
apply the BitRound(5) filter to the large floating point fields (see text for 
details).
For column details, see Table~\ref{tab-genomics-england-data}.
    \label{tab-ofh-data}}
\begin{tabular}{llS[table-format=3.2]S[table-format=4.1]S[table-format=3.2]}
\toprule
{Field} & {Type} & {Storage} & {Compress} & {\% Total} \\
\midrule
/call\_LRR & float32 & 8.41 GiB & 2.9 & 51.65\% \\
/call\_BAF & float32 & 6.14 GiB & 4.0 & 37.71\% \\
/call\_GS & float32 & 1021.24 MiB & 25.0 & 6.12\% \\
/call\_genotype & int8 & 663.97 MiB & 19.0 & 3.98\% \\
/call\_genotype\_mask & bool & 84.7 MiB & 150.0 & 0.51\% \\
/sample\_id & object & 3.19 MiB & 1.6 & 0.02\% \\
/call\_genotype\_phased & bool & 1.08 MiB & 5900.0 & 0.01\% \\
/variant\_id & object & 40.83 KiB & 2.0 & 0.00\% \\
/variant\_position & int32 & 39.03 KiB & 1.0 & 0.00\% \\
/variant\_allele & object & 20.71 KiB & 7.7 & 0.00\% \\
/variant\_filter & bool & 12.55 KiB & 0.8 & 0.00\% \\
/variant\_quality & float32 & 4.51 KiB & 8.8 & 0.00\% \\
/variant\_contig & int8 & 4.51 KiB & 2.2 & 0.00\% \\
/contig\_id & object & 4.51 KiB & 0.0 & 0.00\% \\
/variant\_id\_mask & bool & 4.5 KiB & 2.2 & 0.00\% \\
/contig\_length & int64 & 4.5 KiB & 0.0 & 0.00\% \\
/filter\_id & object & 4.43 KiB & 0.0 & 0.00\% \\
\bottomrule
\end{tabular}
\end{table}

@@

\begin{table}
\caption{Summary for VCF Zarr conversion of 
All of Us exome-like data genotype data for chromosome 22 (245,394 samples, 
715,256 variants) 
consisting of 25 fields and 8.5GiB of storage ($\sim1.1$X larger
% 8.5 / 7.44 = 1.142
than source gzipped VCF).
Here we use the local alleles fields \texttt{call\_LA} and \texttt{call\_LAD};
see text for details.
For column details, see Table~\ref{tab-genomics-england-data}.
\label{tab-auo-data}}
\begin{tabular}{llS[table-format=3.2]S[table-format=4.1]S[table-format=3.2]}
\toprule
{Field} & {Type} & {Storage} & {Compress} & {\% Total} \\
\midrule
/call\_LAD & int16 & 2.26 GiB & 290.0 & 27.85\% \\
/call\_GQ & int8 & 1.89 GiB & 87.0 & 23.29\% \\
/call\_LA & int8 & 1.24 GiB & 260.0 & 15.28\% \\
/call\_genotype & int8 & 914.22 MiB & 370.0 & 11.00\% \\
/call\_RGQ & int16 & 729.57 MiB & 460.0 & 8.78\% \\
/call\_genotype\_mask & bool & 606.02 MiB & 550.0 & 7.29\% \\
/call\_FT & object & 498.61 MiB & 2700.0 & 6.00\% \\
\bottomrule
\end{tabular}
\end{table}
